---
title: "Workflow while using the errorist package"
author: "James Joseph Balamuta"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow while using the errorist package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

The `errorist` package is designed to provide support for newcomers to _R_ who
are learning how to write code. Philosophically, `errorist` takes the position
of being as invisible as possible. To achieve the invisibility, on package load,
handlers to receive error and warning message are automatically created and applied.
These handlers propogate the messages raised by _R_ into the
[`searcher`](https://CRAN.R-project.org/package=searcher) package, which
automatically searches the contents on [Google](https://google.com/) by default.


## Usage 

To use `errorist` in a causal manner, please type:

```{r}
library(errorist)
```

To remove the `errorist` handlers, please either call
the `disable_errorist()` function or detach the package. 

```{r}
detach("package:errorist", unload = TRUE)
```

## Error Search

During development, many issues can arise. With `errorist` enabled, each 
error is automatically searched. For instance, if we typed a function that
wasn't defined, we'd get: 

```r
f()
```

```{r, echo = FALSE}
message('Error in f() : could not find function "f"')
message('Searching query in a web browser ... ')
```

## Warning Search

Outside of errors, the second most common issue is receiving **warnings**.
Warnings only indicate a recoverable issue has occurred during a function run. 
As a result, there can be many warnings that build up during an estimation routine.
If `errorist` is enabled, each unique warning will automatically be searched
within its own tab in the browser. As an example, consider the following function:

```r
many_warnings = function() {
  warning("First warning")
  warning("Second warning")
  warning("Random warning")
  warning("Random warning")
}
```

When run, the `many_warnings()` function will issue exactly **four warnings**. 
However, only three of these warnings are unique. Thus, there will be exactly 
**three** searches performed after the function finishes its execution. As a
result, the output will be like:

```{r, echo = FALSE}
message("Warning messages:")
message("1: In many_warnings() : First warning")
message("2: In many_warnings() : Second warning")
message("3: In many_warnings() : Random warning")
message("Searching query in a web browser ... ")
message("Searching query in a web browser ... ")
message("Searching query in a web browser ... ")
```

