---
title: "Working with the errorist package"
author: "JJB"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Working with the errorist package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The `errorist` package is designed to provide support for newcomers to _R_ who
are learning how to write code. Philosophically, `errorist` takes the position
of being as invisible as possible. To achieve the invisibility, on package load,
handlers to receive error and warning message are automatically created and applied.
These handlers propogate the messages raised by _R_ into the
[`searcher`](https://CRAN.R-project.org/package=searcher) package, which
automatically searches the contents on [Google](https://google.com/) by default.

Thus, to use `errorist` in a causal manner, please type:

```{r}
library(errorist)
```

To remove the `errorist` handlers, please either call
the `disable_errorist()` function or detach the package. 

```{r}
detach("package:errorist", unload = TRUE)
```

